Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/chapters/02-background.tex
Draft of final chapter done

\section{Data Mining}

@@

@@

@@

@@

@@

TODO: linkage and distance

>>>>

\section{Data Mining}
\subsection{Overview}

@@

\subsection{Supervised Learning}

@@

\subsection{Unsupervised Learning}

@@

\subsection{Clustering}

@@

\subsection{Distance and Linkage}

Clustering relies on grouping items that seem close, which creates
a necessity to define what is meant by close. The distance between
any two items is normally determined by a distance
function.\cite{witten2005data} Such a function will normally take
two items and return a value between 0 (items are the same) up to an
an unbounded value as the items are considering further and further
apart.

Related to distance and specific to clustering is the concept of
linkage, which describes the distance between two clusters. A linkage
function will make use of a distance function. Three examples
of linkage functions include:

\begin{itemize}
\item \emph{Complete linkage} between two clusters is defined as the
  greatest distance of all possible pairs of items, one from each
  cluster.
\item \emph{Single linkage} is similar to complete, but the smallest
  distance is used.
\item \emph{Mean linkage} uses the mean where minimum or maximum
  are used above.
\end{itemize}

\subsection{Clustering Media Content}
\label{sec:clustering-media}

@@

In this experiment, Jaccard distance\cite{witten2005data}
based on its suitability for binary, asymmetric data. It is argued
that the vast vocabularly offered by all potential semantic web
RDF triples will lead to very asymmetric binary values based on the
presence or non-presence of that triple.

The chosen linkage function was the complete linkage
on the basis that it ensures that any two content items
within a cluster to be considered related. This avoids the so-called
\emph{chaining phenomenum} where single linkage may create clusters
where two unrelated items are members because they are each related
to an item of chain of related items
therebetween.\cite{everitt2011hierarchical}

### 2016-05-06 report/chapters/04-implementation.tex
Draft of final chapter done

The closeness of two potential, candidate clusters was calculated via
a max linkage on the basis that it ensures that any two content items
within a cluster to be considered related. This avoids the so-called
\emph{chaining phenomenum} where single linkage may create clusters
where two unrelated items are members because they are each related
to an item of chain of related items
therebetween.\cite{everitt2011hierarchical}

The distance between content items was defined by the Jaccard distance
due to its suitability for binary and categorical data.

>>>>

The closeness of two potential, candidate clusters was calculated via
a the complete linkage function as chosen in section~\ref{sec:clustering-media}.
This made use of an implementation of the Jaccard distance as also
justified in that same section.

### 2016-05-06 report/chapters/07-conclusions.tex
Draft of final chapter done

TODO: Build on survey results

\section{Suggestions for Initial Implementations in the Enterprise}

Section~\ref{sec:production-recommendations} covers some recoomedations
for real implementations of semantics for data mining an organisation's
content.

In summary, an organisation can deliver initial value quickly with embedded
semantics (e.g. RDFa) extraction as a general-purpose solution is simple
to implement. The perhaps na\"ive mapping presented in this research for
converting RDF to feature sets performs well enough if the gaps and noise
in the data have a tolerable effect on the outcomes.

Media organisations can iterate very quickly on this simple idea and find
approaches that work for them and at each iteration consider the following:

\begin{itemize}
\item Can we implement entity extraction to supplement the embedded semantics?
\item How do we best tune any entity extaction over time?
\end{itemize}

\section{Future Research}
\subsection{Better Enrichment}
\subsection{Patterns for Reducing Data Noise}
\subsection{Deeper Study of Machine Learning on Semantics}

>>>>

The results of the survey discussed in chapter~\ref{chp:evaluation}
suggest the example application of driving related content suggests
was successful enough to get positive feedback for certain permutations
of the data pipeline. It was argued in analysis of the results that
there is a strong cost-benefit justification in creating a
general-purpose system capable of using embedded semantics on which
a clustering process can at least learn basic categorical structure.
This can then be made more nuanced and topic-drive over time with
entity extraction, when introduced in a supervised way so that it can
be tuned to behave desirably.

The development time on the extraction of embedded semantics is
far less than a series of bespoke enterprise integation efforts
against each data store and there are immediate results in some
of the clusters it can produce.

There is still much need for further research to improve these
extraction processes however. This is discussed in section~\ref{sec:con-future}.

\section{Future Research}
\label{sec:con-future}
\subsection{Better Enrichment}

As discussed in chapter~\ref{chp:evaluation}, enrichment by
deference fell down on some of the drawbacks of extraction via
dereference and did not seem to add much value to the clusters
produced.

The data pipeline designed theoretically in chapter~\ref{chp:design}
described many more suggestions for how we might enrich RDF graphs
in the middle of the pipeline, but this research only allowed time
to experiment with the simplest to implement.

One idea that could have a lot of potential is using OWL and RDFS
ontologies to infer facts not outright stated, which can find
generalisations (e.g. an article about tigers and an article about
lions are both about big cats even if we cannot find the word ``cat''
in their respective text content). Where the application in an
enterprise may be truly powerful is how such reasoning opens up
possibilities to include bespoke business rules to complement the
basic inferences. Here, there are possibilities to find a
balanced compromise from avoiding writing bespoke software to
transform multiple types of content, but still allow for experts
within the organisation to codify their knowledge and guide how the
data is transformed and enriched.

\subsection{Patterns for Reducing Data Noise}

The idea of bespoke inference rules in the previous section can help
reduce noise, but there may be great scope for experimental research
into more generally-applicable ways to strip out semantics we can
broadly identify as not useful for machine learning.

There may be trends or patterns in which vocabularies provide the
most useful data as well. The RDFS and OWL vocabularies focus on
describing ontologies, class hierarchies and schemas, which is more
abstract than describing the actual content and entities therein. Such
research might be able to confirm this is the case and we can indeed
cut back or filter out entirely such vocabularies in favour of, say,
Schema.org that is well-used for describing web content.

\subsection{Deeper Study of Machine Learning on Semantics}

This research presented only clustering as the machine learning
process used for experimentation as the focus was primarily on the
data pipeline upstream of the machine learning itself. Further
research could repeat the same data extraction processes, but explore
which other machine learning algorithms can provide useful insight
into an organisation's content.

Supervised learning techniques could start from known groups of
related content and be trained to identify more of such groups.
Association rule mining could find trends and patterns within
the content.
